---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  fig.width = 5, 
  fig.height = 3, 
  fig.align = "center"
)
```
# distplyr

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.org/vincenzocoia/distplyr.svg?branch=master)](https://travis-ci.org/vincenzocoia/distplyr)
[![Codecov test coverage](https://codecov.io/gh/vincenzocoia/distplyr/branch/master/graph/badge.svg)](https://codecov.io/gh/vincenzocoia/distplyr?branch=master)
[![CRAN status](https://www.r-pkg.org/badges/version/distplyr)](https://CRAN.R-project.org/package=distplyr)
[![License: MIT](https://img.shields.io/badge/license-MIT-blue.svg)](https://cran.r-project.org/web/licenses/MIT)
<!-- badges: end -->

The purpose of `distplyr` is to equip every analyst with a tool to seemlessly draw powerful insights using distributions. Distributions add colour to your analysis. They show the complete picture of uncertainty.

Use `distplyr` to:

- Create and meld distributions using a wide pallet of base forms and tools.
- Draw properties from those distributions.

Many distributions in practice are built in "layers", by transforming and combining other distributions. The result is a tailored distribution that does not follow a basic parametric form such as "Normal" or "Exponential". The motivation behind the name of `distplyr` is that distributions are built by manipulation, akin to the package `dplyr`.

**Note**: This package is still in its infancy. There are many other critical features to come. Expect breaking changes as long as this package is marked as "Experimental".

## Design Choices

`distplyr`:

- Keeps all components of a distribution together in a single object.
- Computes only when needed, by dispatching an appropriate S3 method on call.
- Manages the discrete components of all distributions, often arising from empirical estimates.

## Basic Usage


```{r, warning = FALSE, message = FALSE}
library(distplyr)
```

There are many parametric families of distributions at your disposal. Here is a Uniform distribution:

```{r}
(d1 <- dst_unif(2, 5))
```

Empirical distributions are accomodated, too.

```{r}
(d2 <- stepdst(mpg, data = mtcars))
```


Manipulate distributions. Here's an example of a mixture distribution of two Normals:

```{r, fig.width = 4, fig.height = 3}
(d3 <- mix(
  dst_norm(-5, 1), 
  dst_norm(0, 1), 
  weights = c(1, 4)
))
plot(d3)
```

Generate a sample from a distribution.

```{r}
realise(d3, n = 10)
```


Calculate properties of a distribution. 

```{r}
mean(d1)
variance(d2)
median(d3)
evi(d1)
```

Evaluate distributional representations:

```{r}
eval_density(d1, at = c(2, 3.5, 4.5))
enframe_cdf(d2, at = 1:5)
enframe_hazard(d3, at = 1:5)
```



## Installation

`distplyr` is not on CRAN yet, so the best way to install it is:

``` r
devtools::install_github("vincenzocoia/distplyr")
```


## `distplyr` in Context

`distplyr` is _not_ a modelling package, meaning it won't optimize a distribution's fit to data.

The [`distributions3`](https://cran.r-project.org/web/packages/distributions3/index.html) package is a similar package in that it bundles parametric distributions together using S3 objects, but is less flexible. 

The [`distr`](https://cran.r-project.org/web/packages/distr/index.html) package allows you to make distributions including empirical ones, and transform them, using S4 classes. distplyr aims to provide a simpler interface using S3 objects. 

-----

Please note that the 'distplyr' project is released with a
[Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.

