---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# distplyr

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.org/vincenzocoia/distplyr.svg?branch=master)](https://travis-ci.org/vincenzocoia/distplyr)
[![Codecov test coverage](https://codecov.io/gh/vincenzocoia/distplyr/branch/master/graph/badge.svg)](https://codecov.io/gh/vincenzocoia/distplyr?branch=master)
<!-- badges: end -->

The goal of `distplyr` is to provide a unified interface for distributions by bundling various distributional quantities together, such as a density function, mean, quantiles, and others. It allows you to make non-standard yet useful distributions that go beyond the typical empirical and parametric distributions, by allowing you to combine and/or transform distributions. The name is inspired by the `dplyr` package.

## Usage

```{r, warning = FALSE, message = FALSE}
library(distplyr)
```

Make a Normal distribution with mean 2 and variance 5:

```{r}
(d1 <- dst_norm(2, 5))
```

Evaluate the survival function to obtain the probability of exceeding 6. What about the hazard function at 6?

```{r}
eval_survival(d1, at = 6)
eval_hazard(d1, at = 6)
```

Combine this distribution with another, say to form a mixture distribution:

```{r}
d2 <- dst_norm(-5, 1)
d3 <- mix(d1, d2, probs = c(0.4, 0.6))
plot(get_probfn(d3), -10, 10)
```


What's the mean of the mixture distribution? Standard deviation?

```{r}
get_mean(d3)
get_sd(d3)
```

Generate some data from this new mixture distribution:

```{r}
eval_randfn(d3, at = 10)
```


## `distplyr` in Context

Note that `distplyr` is _not_ a modelling package, meaning it won't optimize a distribution's fit to data.

The [`distributions3`](https://cran.r-project.org/web/packages/distributions3/index.html) package is a similar package in that it bundles parametric distributions together using S3 objects.

The [`distr`](https://cran.r-project.org/web/packages/distr/index.html) package allows you to make distributions including empirical ones, and transform them, using S4 classes. 

-----

Please note that the 'distplyr' project is released with a
[Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.

