---
title: "Manipulating Distributions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Manipulating Distributions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(distplyr)
library(magrittr)
library(tibble)
```

distplyr provides a vocabulary of verbs for manipulating distributions.

**Unary operations:**

- `condition()` (**_under development_**): Restrict the possible values that a random variable can take.
- `+`/`-` or `shift()` (**_under development_**): Add a constant to a random variable.
- `*`/`/` or `scale()` (**_under development_**): Multiply a constant to a random variable.

**Binary operations:**

- `graft_left()` and `graft_right()`: Replace the upper or lower tail of a distribution with another distribution.

**n-ary operations:**

- `mix()`: Make a mixture distribution from two or more distributions. 

Each of these take a distribution as its first argument(s), and return a distribution, making them pipeable.

## Examples

Consider an empirical distribution of Ozone measurements from the `airquality` dataset:

```{r, fig.width = 4, fig.height = 3}
o3_raw <- as_tibble(airquality) %>% 
  dst_empirical(Ozone, data = .)
```

We can graft a GPD to either end:

```{r}
o3_with_tails <- o3_raw %>% 
  graft_right(dst_gpd(100, 30, 1), sep_y = 100)
plot(o3_raw, "survival", n = 1001, to = 160)
plot(o3_with_tails, "survival", n = 1001, lty = 2, add = TRUE)
```



