---
title: "Probing a Distribution"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Probing a Distribution}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE}
knitr::opts_chunk$set(fig.width = 5, fig.height = 3, fig.align = "center")
```

```{r}
library(distplyr)
```


One purpose of `distplyr` is to handle the menial distribution-related calculations for you. Just specify a distribution once, and there is no need to manage its components anymore. 

## Functional Representations of a Distribution

A distribution can be represented by different functions. In `distplyr`, you can either evaluate the function directly by calling `eval_*`, or get the function itself using `get_*`. Here are the representations and the corresponding `distplyr` functions:  

| Quantity                            | `distplyr` Function               |
|-------------------------------------|-----------------------------------|
| Cumulative Distribution Function    | `eval_cdf()`,    `get_cdf()`    |
| Survival Function                   | `eval_survival()`,    `get_survival()`    |
| Quantile Function                   | `eval_quantile()`, `get_quantile()` |
| Hazard Function                     | `eval_hazard()`,   `get_hazard()`   |
| Cumulative Hazard Function          | `eval_chf()`,     `get_chf()`     |
| Probability (mass/density) function | `eval_probfn()`,  `get_probfn()`  |
| Random sample generator             | `eval_randfn()`,  `get_randfn()`  |

Both the `eval_*` and `get_*` functions take a distribution object as their first argument, but `eval_*` has a second argument named `at` indicating where to evaluate the function. The `at` argument is vectorized, except for `eval_randfn()`, which returns a vector of a random sample of the length that you specify. 

Here is an example of evaluating the hazard function and the random sample generator of a Uniform(0,1) distribution:

```{r}
d <- dst_unif(0, 3)
eval_hazard(d, at = 0:10)
set.seed(10)
eval_randfn(d, at = 5)
```


## Properties of Distributions

Distributions have various numeric properties. Common examples are the mean and variance, but there are many others as well. 

Below is a table of the properties incorporated in `distplyr`:

| Property | `distplyr` Function |
|----------|---------------------|
| Mean                       | `get_mean()` |
| Median                     | `get_median()` |
| ~~Mode~~                       | ~~`get_mode()`~~ |
| Variance                   | `get_variance()` |
| Standard Deviation         | `get_sd()` |
| ~~Inter-Quartile Range~~       | ~~`get_iqr()`~~ |
| ~~Entropy~~                    | ~~`get_entropy()`~~ |
| Skewness                   | `get_skewness()` |
| Excess Kurtosis            | `get_kurtosis_exc()` |
| Kurtosis                   | `get_kurtosis_raw()` |
| Extreme Value (Tail) Index | `get_evi()` |

Here are some properties of a certain mixture of Gaussians:

```{r}
m <- mix(dst_norm(0, 1), dst_norm(5, 1), probs = c(0.2, 0.8))
get_mean(m)
get_sd(m)
get_evi(m)
```


