---
title: "Probing a Distribution"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Probing a Distribution}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE}
knitr::opts_chunk$set(fig.width = 5, fig.height = 3, fig.align = "center")
```

```{r}
library(distplyr)
```


One purpose of `distplyr` is to handle the menial distribution-related calculations for you. Just specify a distribution once, and there is no need to manage its components anymore. 

## Functional Representations of a Distribution

A distribution can be represented by different functions. In `distplyr`, you can: 

- evaluate the function directly by calling `eval_*`;
- evaluate the function and enframe results together with the function arguments with `enframe_*`; or 
- get the function itself using `get_*`. 

Here are the representations and the corresponding `distplyr` functions:  

| Quantity                         | `distplyr` Functions              |
|----------------------------------|-----------------------------------|
| Cumulative Distribution Function | `eval_cdf()`,      `get_cdf()`,      `enframe_cdf()`      |
| Survival Function                | `eval_survival()`, `get_survival()`, `enframe_survival()` |
| Quantile Function                | `eval_quantile()`, `get_quantile()`, `enframe_quantile()` |
| Hazard Function                  | `eval_hazard()`,   `get_hazard()`,   `enframe_hazard()`   |
| Cumulative Hazard Function       | `eval_chf()`,      `get_chf()`,      `enframe_chf()`      |
| Probability density function     | `eval_density()`,  `get_density()`,  `enframe_density()`  |
| Probability mass function        | `eval_pmf()`,      `get_pmf()`,      `enframe_pmf()`      |
| Random sample generator          | `realise()`, `realize()`  |

These functions all take a distribution object as their first argument, and `eval_*` and `enframe_*` have a second argument named `at` indicating where to evaluate the function. The `at` argument is vectorized.

Note that all of the `stats::p*/d*/q*/r*` functions are included in this list of representations, except for the `r` functions (such as `rnorm()`, `rpois()`, etc.). These `r` functions generate a random sample, which cannot be used to reconstruct a distribution exactly, and are therefore omitted in the list of representations. Instead, use the `realise()` or `realize()` function.

Here is an example of evaluating the hazard function and the random sample generator of a Uniform(0,1) distribution:

```{r}
d <- dst_unif(0, 3)
eval_hazard(d, at = 0:10)
set.seed(10)
realise(d, n = 5)
```


## Properties of Distributions

Distributions have various numeric properties. Common examples are the mean and variance, but there are many others as well. 

Below is a table of the properties incorporated in `distplyr`:

| Property | `distplyr` Function |
|----------|---------------------|
| Mean                       | `get_mean()` |
| Median                     | `get_median()` |
| ~~Mode~~                       | ~~`get_mode()`~~ |
| Variance                   | `get_variance()` |
| Standard Deviation         | `get_sd()` |
| ~~Inter-Quartile Range~~       | ~~`get_iqr()`~~ |
| ~~Entropy~~                    | ~~`get_entropy()`~~ |
| Skewness                   | `get_skewness()` |
| Excess Kurtosis            | `get_kurtosis_exc()` |
| Kurtosis                   | `get_kurtosis_raw()` |
| Extreme Value (Tail) Index | `get_evi()` |

Here are some properties of a certain mixture of Gaussians:

```{r}
m <- mix(dst_norm(0, 1), dst_norm(5, 1), weights = c(1, 4))
get_mean(m)
get_sd(m)
get_evi(m)
```


