---
title: "Step Distributions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Step Distributions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE}
knitr::opts_chunk$set(fig.width = 5, fig.height = 3, fig.align = "center")
```

A common way of representing data is through a parametric distribution, such as a Normal distribution, Exponential, Poisson, and others. A useful alternative is to use an empirical distribution, or in general what `distplyr` calls a _step distribution_.

To make a step distribution, use the function `stepdst()`:

```{r}
library(distplyr)
(d1 <- stepdst(hp, data = mtcars))
```

The "step" in the name comes from the cdf:

```{r}
plot(d1, "cdf", n = 1001)
```

You can also weigh the outcomes differently. This is useful for explicitly specifying a probability mass function, as well as for other applications such as using kernel smoothing to find a conditional distribution. Here is an estimate of the conditional distribution of `hp` given `disp = 150`, with cdf depicted as the dashed line compared o the marginal with the solid line:

```{r}
K <- function(x) dnorm(x, sd = 25)
d2 <- stepdst(hp, data = mtcars, weights = K(disp - 150))
plot(d1, "cdf", n = 1001)
plot(d2, "cdf", n = 1001, lty = 2, add = TRUE)
```

This is much more informative compared with a point prediction of `hp` when `disp = 150`. Such a prediction might be:

```{r}
get_mean(d2)
```

With a distribution, you can get much more, such as a prediction interval. Here's a 90% interval:

```{r}
eval_quantile(d2, at = c(0.05, 0.95))
```

Here's the proportion of variance that's reduced compared to the marginal:

```{r}
1 - get_variance(d2) / get_variance(d1)
```

You can extract the step discontinuities in any distribution, using the `discontinuities()` function. It will give you the location of the discontinuities, and the size of the jump in the cdf:

```{r}
discontinuities(d2)
```

For continuous distributions, there are no discontinuities:

```{r}
discontinuities(dst_norm(0, 1))
```


