---
title: "Step Distributions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Step Distributions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE}
knitr::opts_chunk$set(fig.width = 5, fig.height = 3, fig.align = "center")
```

A common way of representing data is through a parametric distribution, such as a Normal distribution, Exponential, Poisson, and others. A useful alternative is to use an empirical distribution, or in general what `distplyr` calls a _step distribution_.

To make a step distribution, use the function `stepdst()`:

```{r}
library(distplyr)
(d1 <- stepdst(mpg, data = mtcars))
```

The "step" in the name comes from the cdf:

```{r}
plot(d1, "cdf", n = 1001)
```

You can also weigh the outcomes differently:

```{r}
(d2 <- stepdst(1:4, weights = c(1, 2, 1, 2)))
plot(d2, "cdf", n = 1001)
```

You can extract the step discontinuities in any distribution, using the `discontinuities()` function. It will give you the location of the discontinuities, and the size of the jump in the cdf:

```{r}
discontinuities(d2)
```

For continuous distributions, there are no discontinuities:

```{r}
discontinuities(dst_norm(0, 1))
```


